Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-02 WSSSPE3/report/wg_main_funding_spec_expert.tex
Make minor changes to remind me which files to editå

\subsection{White paper/journal paper about best practices in developing sustainable software}
\label{sec:best-practices}

@@

[15 Nov] Introduction and scope finished
[15 Nov] Sections assigned
[31 Jan] Analysing funding possibilities for survey
[31 Jan] First versions of section
[15 Feb] Distribution to WSSSPE community
[31 Mar] Final version of white paper
[30 Apr] Submission of peer-reviewed paper?

\begin{enumerate}
\item Introduction and Scope of White Paper 
\item Related Work
\item Case Studies
\begin{enumerate} 
\item PeTSC
\item NWCHEM
\item CIG
\end{enumerate}
\item Community Related Practices
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Governance and management
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Funding Related
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Metrics for sustainability
\item Tools
\item Conclusions
\end{enumerate}

>>>>

\subsection{Research Programming Expertise -- how to fund it and sustain it.}

@@
